Data Management \\ and LSST Special Programs

### 2021-11-27 DMTN-065.tex
removed refs to white papers up to S3.1

\documentclass[DM,lsstdoc,toc]{lsstdoc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{latexsym}
\usepackage{color}
% black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, magenta, blue, orange, pink, purple, red, teal, violet, white, yellow.
\usepackage{enumitem}

@@

\setDocAbstract{This document provides an in-depth description of the role of the LSST Project in preparing software and providing computational resources to process the data from Special Programs (deep drilling fields and/or mini-surveys). The plans and description in this document flow down from the requirements in \citeds{LSE-61} regarding processing for Special Programs. The main target audience is the LSST Data Management (DM) team, but members of the community who are preparing white papers on science-driven observing strategies may also find this document useful. The potential diversity of data from Special Programs is summarized, including boundaries imposed by technical limitations of the LSST hardware. The capability of the planned Data Management system to processes this diversity of Special Programs data is the main focus of this document. Case studies are provided as examples of how the LSST software and/or user-generated pipelines may be combined to process the data from Special Programs.}

@@

The main LSST science goals will be met by the Wide-Fast-Deep (WFD) Main Survey, but this is expected to be accomplished with $85$--$90$\% of the observing time available over the $10$ year survey. The remaining $10$--$15$\% of the time will be spent on Special Programs: alternative survey areas and/or observing strategies driven by a specific science goal. A call for white papers that provide scientific motivation and observing strategies for the WFD survey and Special Programs, \citeds{Document-28382}, released in June 2018, has a deadline of November 30 2018. It is conceivable that Special Programs might obtain imaging data that are significantly different from the WFD main survey, and/or requires special processing in order to achieve the program's science goals. This document provides an in-depth description of the role of the LSST Project in preparing to process the data from Special Programs (expanding on the general description in Section 6 of \citeds{LSE-163}). The main target audience is the LSST Data Management (DM) team, but members of the science community who are preparing white paper proposals may also find this document useful.

@@

{\bf Document Overview -- } The purpose of this document is to assess the potential diversity of imaging data that might be obtained by Special Programs (Section \ref{sec:data}), and to explore and clarify whether -- and to what extent -- DM's planned pipelines and user services will be able to handle this diversity of data (Section \ref{sec:dmplans}). As described in the call for white papers on cadence optimization (\citeds{Document-28382}), Special Programs that may require specialized or computationally-intense algorithms to meet their science goals are required to describe how these processing needs will be met. Sections \ref{sec:data} and \ref{sec:dmplans} have been designed to help white paper authors figure out whether their proposed Science Program(s) require processing that would be considered out of DM's scope, and in Section \ref{sec:SPCS} we have provided a series of science-driven case studies as examples.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\clearpage
\section{The Potential Diversity of Special Programs Data} \label{sec:data}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\clearpage
\section{Processing Special Programs Data with LSST DM Pipelines} \label{sec:dmplans}

>>>>

\documentclass[DM,lsstdoc,toc]{lsstdoc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{latexsym}
% \usepackage{color}
% black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, magenta, blue, orange, pink, purple, red, teal, violet, white, yellow.
\usepackage{enumitem}

@@

\setDocAbstract{
This document provides an in-depth description of the role of the LSST Project in preparing software and providing computational resources to process the data from Special Programs (deep drilling fields and/or mini-surveys).
The plans and description in this document flow down from the requirements in \citeds{LSE-61} regarding processing for Special Programs.
The main target audience is the LSST Data Management (DM) team, but members of the community who are planning to use Special Programs to reach their science goals may also find this document useful.
The potential diversity of data from Special Programs is summarized, including boundaries imposed by technical limitations of the LSST hardware.
The capability of the planned Data Management system to processes this diversity of Special Programs data is the main focus of this document.
Case studies are provided as examples of how the LSST software and/or user-generated pipelines may be combined to process the data from Special Programs.}

@@

The main LSST science goals will be met by the Wide-Fast-Deep (WFD) Main Survey, but this is expected to be accomplished with $85$--$90$\% of the observing time available over the $10$ year survey.
The remaining $10$--$15$\% of the time will be spent on Special Programs: alternative survey areas and/or observing strategies driven by a specific science goal.
%A call for white papers that provide scientific motivation and observing strategies for the WFD survey and Special Programs, \citeds{Document-28382}, released in June 2018, has a deadline of November 30 2018.
It is conceivable that Special Programs might obtain imaging data that are significantly different from the WFD main survey, and/or requires special processing in order to achieve the program's science goals.
This document provides an in-depth description of the role of the LSST Project in preparing to process the data from Special Programs (expanding on the general description in Section 6 of \citeds{LSE-163}).
The main target audience is the LSST Data Management (DM) team, but members of the science community who are preparing white paper proposals may also find this document useful.

@@

{\bf Document Overview -- }
The purpose of this document is to assess the potential diversity of imaging data that might be obtained by Special Programs (Section \ref{sec:data}), and to explore and clarify whether -- and to what extent -- DM's planned pipelines and user services will be able to handle this diversity of data (Section \ref{sec:dmplans}). 
Special Programs that may require specialized or computationally-intense algorithms to meet their science goals are required to describe how these processing needs will be met.
Sections \ref{sec:data} and \ref{sec:dmplans} have been designed to help the science community figure out whether proposed Science Program(s) require processing that would be considered out of DM's scope, and in Section \ref{sec:SPCS} we have provided a series of science-driven case studies as examples.

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\clearpage
\section{The Potential Diversity of Special Programs Data} \label{sec:data}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\clearpage
\section{Processing Special Programs Data with LSST DM Pipelines} \label{sec:dmplans}
